---
title: "Lab1"
output: html_document
---

1.  Import data set "cars" from .csv file to R.

    ```{r}
    cars <- read.csv("cars.csv")
    head(cars)
    ```

2.  Summarize the data. How many quantitative and qualitative variables are there in the data set?

    ```{r}

    summary(cars)
    ```

    ```{r}
    summary(cars)
    ```

    `brand` and `cylinders` are quantitative variables

    ```{r}
    cars = read.csv("cars.csv", stringsAsFactors = TRUE)
    summary(cars)

    cars$brand = as.factor(cars$brand)
    cars$cylinders = as.factor(cars$cylinders)

    summary(cars)
    ```

<!-- -->

3.  Visualize the distribution of the following variables by using a proper chart and interpret the findings:

    -   year

    -   brand

    -   mpg

    -   hp

    -   weight

    ```{r}
    summary(cars$year)
    ```

    ```{r}
    cars$years = as.factor(cars$year)

    barplot(summary(cars$years), xlab = "year")
    ```

    ```{r}
    barplot(summary((cars$brand)), xlab = "Brand")
    ```

    ```{r}
    hist(cars$mpg, xlab = "mpg")
    ```

    ```{r}
    hist(cars$hp, xlab = "hp")
    ```

    ```{r}
    hist(cars$weightlbs, xlab = "weight")
    ```

4.  Construct a descriptive statistics table with mean, median and standard deviation for the variables mpg, hp and weight.

    ```{r}
    #str(cars)

    for (i in 2:6) {
      cars[,i] = as.numeric(cars[,i])
    }

    #str(cars)

    apply(cars[,c(1,4,5)], 2, mean, na.rm = TRUE)

    avr = apply(cars[,2:6], 2, mean, na.rm = TRUE)
    med = apply(cars[,2:6], 2, median, na.rm = TRUE)
    std = apply(cars[,2:6], 2, sd, na.rm = TRUE)

    tab = rbind.data.frame(avr, med, std)
    rownames(tab) = c("mean", "median", "std. dev.")
    colnames(tab) = names(avr)
    tab
    ```

5.  Compare the distribution of weight across car brands. Visualize it by using a box plot.

    ```{r}
    boxplot(cars$weightlbs ~ cars$brand, xlab = "Weight across car brans")
    ```
